### 2023-01-24 README.Rmd
updated readme
...

```{r, eval=FALSE}
# colorspace 2.1 required:
install.packages(https://rdrr.io/r/utils/install.packages.html)("colorspace", repos = "https://R-Forge.R-project.org")

@@

*   `c4a_palettes` Get available palette names
*   `c4a_series` Get available series names
*   `c4a_citation` Show how to cite palettes (with bibtex code).
*   `c4a_info` Get information from a palette, such as type and maximum number
    of colors
*   `.P` Environment via which palette names can be browsed with
    auto-completion (using `$`)

>>>>

```{r, eval=FALSE}
# colorspace 2.1 required:
install.packages("colorspace", repos = "https://R-Forge.R-project.org")

@@

*   `c4a_palettes` Get available palette names
*   `c4a_series` Get available series names
*   `c4a_types` Get implemented types
* 	`c4a_overview` Get an overview of palettes per series x type.
*   `c4a_citation` Show how to cite palettes (with bibtex code).
*   `c4a_info` Get information from a palette, such as type and maximum number
    of colors
*   `.P` Environment via which palette names can be browsed with
    auto-completion (using `$`)
